Notes on Matrix Factorization for Hartree-Fock Stability of HEG

### 2017-02-13 doc/papers/matrixproperties/MatrixProperties.tex
got out of the pickle
Edited the matrixproperties a bit and a few parameters testing
Add stability equation derivation mathematica notebook
A few more tweaks and the entirety of the stability derivations
will be in the notebook.

\definecolor{myred}{HTML}{CC5803}
\definecolor{myblue}{HTML}{204B57}

\newcommand{\Ap}{\textcolor{myred}{\braket{aj|ib}}}
\newcommand{\App}{\textcolor{myred}{\braket{aj|bi}}}
\newcommand{\Aa}{\textcolor{myred}{\braket{aj||ib}}}
\newcommand{\B}{\textcolor{myblue}{\braket{ab|ij}}}
\newcommand{\Br}{\textcolor{myblue}{\braket{ab|ji}}}
\newcommand{\Ba}{\textcolor{myblue}{\braket{ab||ij}}}

@@

\section{Orbital Hessian Factorization}
According to Seeger and Pople\cite{Seeger1977}, (and many other sources) the molecular orbital
Hessian has the form,
\begin{eqnarray*}
\mathbf{H} =
  \begin{bmatrix}
    \mathbf{A}   & \mathbf{B}   \\
    \mathbf{B^*} & \mathbf{A^*} \\
  \end{bmatrix}
\end{eqnarray*}

Where the matrices denoted by $\mathbf{A}$ and $\mathbf{B}$ are given by,

\begin{eqnarray*}
  A_{st} &=& \e\diag -  \Aa \\
  B_{st} &=& \Ba         \\
\end{eqnarray*}

The color is to help keep track of which portions of the matrices come from
$\mathbf{A}$ and $\mathbf{B}$.
The integration is over spin and spatial coordinates. In the case of
a stationary UHF solution, the matrices $\mathbf{A}$ and $\mathbf{B}$ have the
following forms, after integrating over spin:

\begin{eqnarray*}
  \mathbf{A}&=&\kbordermatrix{
        & \AtoA           & \AtoB           & \BtoA          & \BtoB          \\
  \AtoA & \e\diag + \Aa   & 0               & 0              & \Ap            \\
  \AtoB & 0               & \e\diag - \App  & 0              & 0              \\
  \BtoA & 0               & 0               & \e\diag - \App & 0              \\
  \BtoB & \Ap             & 0               & 0              & \e\diag + \Aa  \\
}
\end{eqnarray*}

\begin{eqnarray*}
  \mathbf{B}&=&\kbordermatrix{
        & \AtoA           & \AtoB           & \BtoA          & \BtoB          \\
  \AtoA & \Ba             & 0               & 0              & \B             \\
  \AtoB & 0               & 0               & -\Br           & 0              \\
  \BtoA & 0               & -\Br            & 0              & 0              \\
  \BtoB & \B              & 0               & 0              & \Ba            \\
}
\end{eqnarray*}
\\
These matrices factorize into ``spin conserved'' $(\mathbf{A', B'})$ and
``spin-unconserved'' $(\mathbf{A'', B''})$ parts, to use the language of Seeger
and Pople. The spin conserved matrices are given by

>>>>

\definecolor{myred}{HTML}{990000}
\definecolor{myblue}{HTML}{002299}

\newcommand{\Ap}{\textcolor{myred}{\left(aj|ib\right)}}
\newcommand{\App}{\textcolor{myred}{\left(aj|bi\right)}}
\newcommand{\Aa}{\textcolor{myred}{\left(aj||ib\right)}}
\newcommand{\B}{\textcolor{myblue}{\left(ab|ij\right)}}
\newcommand{\Br}{\textcolor{myblue}{\left(ab|ji\right)}}
\newcommand{\Ba}{\textcolor{myblue}{\left(ab||ij\right)}}

@@

\section{Orbital Hessian Factorization}
According to Seeger and Pople\cite{Seeger1977}, (and many other sources) the molecular orbital
Hessian has the form,
\begin{eqnarray*}
\mathbf{H} =
  \begin{bmatrix}
    \mathbf{A}   & \mathbf{B}   \\
    \mathbf{B^*} & \mathbf{A^*} \\
  \end{bmatrix}
\end{eqnarray*}
Where the matrices denoted by $\mathbf{A}$ and $\mathbf{B}$ are given by,
\begin{eqnarray*}
  A_{st} &=& \e\diag +  \textcolor{myred}{\braket{aj||ib}} \\
  B_{st} &=& \textcolor{myblue}{\braket{ab||ij}}         
\end{eqnarray*}
The color is to help keep track of which portions of the matrices come from
$\mathbf{A}$ and $\mathbf{B}$.
The integration is over spin and spatial coordinates. In the case of
a stationary UHF solution, the matrices $\mathbf{A}$ and $\mathbf{B}$ have the
following forms, after integrating over spin:
\begin{eqnarray*}
  A_{st} &=& \e\diag \textcolor{myred}{+ \delta_{\sigma_i\sigma_a}\delta_{\sigma_j\sigma_b}\Ap
                     - \delta_{\sigma_a\sigma_b}\delta_{\sigma_i\sigma_j}\App} \\
  B_{st} &=& \textcolor{myblue}{\delta_{\sigma_a\sigma_i}\delta_{\sigma_b\sigma_j}\B 
             - \delta_{\sigma_a\sigma_b}\delta_{\sigma_i\sigma_j}\Br} 
\end{eqnarray*}
In matrix form, 
\begin{eqnarray*}
  \mathbf{A}&=&\kbordermatrix{
        & \AtoA           & \AtoB           & \BtoA          & \BtoB          \\
  \AtoA & \e\diag + \Aa   & 0               & 0              & \Ap            \\
  \AtoB & 0               & \e\diag - \App  & 0              & 0              \\
  \BtoA & 0               & 0               & \e\diag - \App & 0              \\
  \BtoB & \Ap             & 0               & 0              & \e\diag + \Aa  
}
\end{eqnarray*}
\begin{eqnarray*}
  \mathbf{B}&=&\kbordermatrix{
        & \AtoA           & \AtoB           & \BtoA          & \BtoB          \\
  \AtoA & \Ba             & 0               & 0              & \B             \\
  \AtoB & 0               & 0               & -\Br           & 0              \\
  \BtoA & 0               & -\Br            & 0              & 0              \\
  \BtoB & \B              & 0               & 0              & \Ba            
}
\end{eqnarray*}
\\
These matrices factorize into ``spin conserved'' $(\mathbf{A', B'})$ and
``spin-unconserved'' $(\mathbf{A'', B''})$ parts, to use the language of Seeger
and Pople. The spin conserved matrices are given by
